%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Do not alter this block of commands.  If you're proficient at LaTeX, you may include additional packages, create macros, etc. immediately below this block of commands, but make sure to NOT alter the header, margin, and comment settings here. 
\documentclass[12pt]{article}
 \usepackage{geometry} 
\usepackage{amsmath,amsthm,amssymb,amsfonts, enumitem, fancyhdr, color, comment, graphicx, environ,multicol}
\pagestyle{fancy}
%\setlength{\headheight}{65pt}
\newenvironment{problem}[2][Problem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{sol}
    {\emph{Solution:}
    }
    {
    \qed
    }
\specialcomment{com}{ \color{blue} \textbf{Comment:} }{\color{black}} %for instructor comments while grading
\NewEnviron{probscore}{\marginpar{ \color{blue} \tiny Problem Score: \BODY \color{black} }}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Fill in the appropriate information below
\lhead{Student's name}  %replace with your name
\rhead{Homework 5} %replace XYZ with the homework course number, semester (e.g. ``Spring 2019"), and assignment number.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\everymath{\displaystyle}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Do not alter this block.
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{problem}{1}
  \begin{enumerate}[label=\roman*)]
  \item The sum of two numbers is 50 and their difference is 22. Find the numbers.
  \item One number is three times the other number. The difference between the two numbers is 12. Find the two numbers.
  \item The difference between the two numbers is 7. Two times the smaller number added to the larger number gives 22. Find the two numbers.
  \item Ten years ago, mother was 12 times as old as her daughter and ten years, hence she will be twice as old as her daughter will be. Find the present ages.
    \item Two hundred eighty-two people attended a recent performance of Cinderella. Adult tickets sold for \$5
and children’s tickets sold for \$3 each. Find the number of adults and the number of children that attended
the play if the total revenue was \$1046. 
  \item The sum of two numbers is 14 and their difference is 2, find the numbers.
  \item In a two digit number. The units digit is thrice the tens digit. If 36 is added to the number, the digits interchange their place. Find the number.
    
  \item If twice the age of son is added to age of father, the sum is 56. But if twice the age of the father is added to the age of son, the sum is 82. Find the ages of father and son. 

  \end{enumerate}

\end{problem}
%\begin{sol}
%Write your solution here.
%\end{sol}



%Copy the following block of text for each problem in the assignment.
\begin{problem}{2}
  Solve,
  \begin{multicols}{2}
  \begin{enumerate}[label=\roman*)]
  \item $(k+1)(k-5) = 0$
  \item $(4k+5)(k+1)=0$
  \item $x^2 - 11 + 19=-5$
  \item $n^2 + 8n = -15$
  \item $5r^2-44r + 120 = -30+11r$
  \item $35k^2 - 22k + 7=4$
  \item $10b^2 = 27 b -18$
  \item $(x-10)^2 - 48 = 0$
  \item $x^2 + 14x + 45=0$
  \item $4x^2-100=0$
  \item $6x^2-48x-54=0$
  \item $9x^2+7x-4=0$
  \item $3x^2+9x-6=0$
  \item $4(x+3)^2-3=17$
  \item $ (2x-5)^2-180=0$
  \item $(4x-1)(2x-3)=-2$
  \item $y^2+(y+1)^2 = 41$
  \end{enumerate}
\end{multicols}
\end{problem}

\begin{problem}{3}
  \begin{enumerate}[label=\roman*)]
  \item If 2 is one of the solutions of the equation $x^2-8x+k=0$, find $k$ and the other solution.
    \item if -3 is one of the solutions of the equation $x^2-kx+3=0$, find $k$ and the other solution.
  \item The width of a rectangle is 5 feeet less than half of its length.  Find the dimensions of the rectangle if its area is 48 ft$^2$.
  \item The height of a triangle is 5 cm more than double its base.  Find the base if the area of the triangle is 450 cm$^2$.
  \item Find the perimeter of a rectangle whose area is 80 in$^2$ and its width his 11 inches less than its length.
    \item The product of two positive consecutive odd integers is 2499.  

  \end{enumerate}

\end{problem}


\noindent {\large \bf In addition}

\noindent In addition to the above the student is responsible for completing All problems in section 3.4.


%\begin{sol}
%Write your solution here.
%\end{sol}

%% \begin{problem}{5} Simplify
%%  \begin{multicols}{2}
%%    \begin{enumerate}[label=\roman*)]
%%    \item $\left(\frac{1}{x}+\frac{1}{y}\right)\div(x^2-y^2)$
%%    \item $\left(\frac{1}{x-1}-\frac{1}{x+1}\right)\div\frac{1-x^2}{x}$
%%    \item $\frac{1}{x-1}-\frac{1}{x+1}\div\frac{1-x^2}{x}$
%%    \item $\frac{1}{x-1}-\frac{1}{x+1}\cdot\frac{1-x^2}{x}$
%%    \item $\left(\frac{1}{x-1}-\frac{1}{x+1}\right)\cdot\frac{1-x^2}{x}$
%%    \item $\frac{\displaystyle\frac{1}{1-x}-\frac{1}{x}}{\displaystyle\frac{1}{1-x^2}}$
%%      \item $\frac{\displaystyle 1 -\frac{7}{y}+\frac{12}{y^2}}{\displaystyle 1+\frac{1}{y}-\frac{20}{y^2}}$
%%   \end{enumerate}
%%  \end{multicols}
%% \end{problem}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Do not alter anything below this line.
\end{document}
